\section*{Acknowledgements}

I want to thank all people that helped me actively and passively for making this thesis possible.

In the first place I want to express my gratitude to my advisors Felix Kosmalla and Dr. Florian Daiber for providing me with helpful and competent advises for this topic, arranging all the hardware I needed, preparing the conducted study, proofreading my thesis, and lastly for supporting me in every situation during the entire time. Further, I want to thank Prof. Dr. Antonio Krüger for the opportunity to work on this interesting topic and I also want to thank Dr. Jürgen Steimle for having interest in this thesis and for being my second supervisor.

I also would like to specially thank Tobias Walter and Maximilian Mock for supporting me in every way during all the time, reviewing my thesis, and all the helpful discussions.
In addition, I want to thank Patrick Schuck for his helpful advises concerning the statistical analysis of the study.

A thank goes to all people that participated in the study.

Lastly, I especially thank my family and friends who have supported, understood, and motivated me throughout the entire period.

\begin{comment}
Thanks to:
\begin{itemize}
\item Prof
\item Advisors
\item Tobias Walter
\item Family
\item Everyone else
\item Maybe avarteq
\end{itemize}

Thank for:
\begin{itemize}
\item Help regarding research
\item Be able to write the thesis in here
\item Organizing and getting hardware and stuff for thesis
\item Supporting me in all things regarding conceptual, design related, technical and reviewing stuff
\item Mental and pushing me forward
\item Avarteq for letting me have time to write the thesis
\end{itemize}
\end{comment}