\chapter{Study}\label{6_study}
%The interactive slackline system should be  in an \todo{explorative?} user study. 
%The elaboration, preparation, execution, measurement, and analysis is part of this chapter. 
This chapter describes the conducted study in detail. 
At first, the idea of the study is introduced and its hypothesis as well as the purpose clarified in section \textit{\nameref{6_introduction}}.
After that, section \textit{\nameref{6_participants}} provides information about the trainees that have participated in the study.
Further, section \textit{\nameref{6_method}} describes the conditions, apparatus, design, procedure, and the independent and dependent variables.
%shows how the tested methods are constructed. The procedure of the study consists of several parts, like the briefing, measurements, experiment itself, and an interview. This is discussed in detail within section \todo{structure}. 
Along with that, the outcome of the study is elaborated in section \textit{\nameref{6_results}}.
At last, these results are discussed in section \textit{\nameref{6_discussion}}.
\begin{comment}
This chapter describes the idea and procedure of the conducted study in detail.
At first, the introduction and goals are clarified.
After that, information about the participants is given.
In the following, the structure of the study is described, which includes the different conditions, apparatus, design, procedure, and the independent and dependent variables.
Along with that, the results are analysed and their outcome discussed.
\end{comment}
The conducted study has its main purpose to test whether the SLS can 
This chapter describes the idea and procedure of the conducted study in detail.

\input{Chapter/6_Study/1_ResearchQuestions}
\input{Chapter/6_Study/2_Participants}
\input{Chapter/6_Study/3_Methods}
\input{Chapter/6_Study/4_ResultsAnalysis}
\input{Chapter/6_Study/5_Discussion}
