\chapter{Concept}
In chapter \textit{\nameref{2_relatedWork}} and \textit{\nameref{3_slacklining}} chapter is described how other applications realized similar application with other activities, what slacklining in particular is and which learning techniques exist to learn and master it. Mostly this is done with a professional who already knows how to act on the line and where particular attention must be paid. In contrast to such a human personal trainer this thesis will elaborate an interactive slackline learning system with real-time feedback. The idea of this system is, that the user can learn slacklining only with the given application. One main feature is that it should be an autonomous system. This gives the opportunity to be independent of other human help and therefore it can only 
be controlled by the by the user that is currently interacting with the system. To help her with exercise execution it responds to the actions of the user and provides him with feedback such that the user can correct himself. To built such a system a concept has to be built, which is part of this chapter. Therefore in the following a conceptual analysis will be elaborated. It involves section \textit{\nameref{4_1_general}} where basic requirements of the entire system are described. This is followed by the more specific sections \textit{\nameref{4_2_interaction}}, \textit{\nameref{4_3_stages}} and \textit{\nameref{4_4_exercises}} as well as \textit{\nameref{4_5_feedbackSystem}}. These describe how feedback is properly given to the user. Lastly the section \textit{\nameref{4_6_scenario}} gives a good overview about the worflow of the particular components and \textit{\nameref{4_7_conclusion}} will wrap up of each part of the concept.
\input{Chapter/4_Concept/1_General}
\input{Chapter/4_Concept/2_Interaction}
\input{Chapter/4_Concept/3_Stages}
\input{Chapter/4_Concept/4_Exercises}
\input{Chapter/4_Concept/5_FeedbackSystem}
\input{Chapter/4_Concept/6_Scenario}
\input{Chapter/4_Concept/7_Conclusion}